### 2011-05-10 paper.tex
Made definition style consistent

\begin{definition}\label{partialfunction}
A \emph{partial function} is a function $f: \bigcup_{n=0}^{\infty}\{0,1\}^n \to \{0,1,\x\}$.
\end{definition}

@@

\begin{definition}\label{complexityclass}
A \emph{complexity class} is a set of partial functions.
\end{definition}

\begin{definition}\label{p}
The complexity class $\p$ is the set of partial functions such that $f \in \p$ if and only if there exists a polynomial $p$ and a Turing machine $T$ such that:
\begin{itemize}
\item If $f(x) = 1$, then $T$ halts after at most $p(|x|)$ steps and accepts.
\item If $f(x) = 0$, then $T$ halts after at most $p(|x|)$ steps and rejects.
\end{itemize}
\end{definition}

>>>>

\begin{definition}\label{partialfunction}
\emph{
A \emph{partial function} is a function $f: \bigcup_{n=0}^{\infty}\{0,1\}^n \to \{0,1,\x\}$.
}
\end{definition}

@@

\begin{definition}\label{complexityclass}
\emph{
A \emph{complexity class} is a set of partial functions.
}
\end{definition}

\begin{definition}\label{p}
\emph{
The complexity class $\p$ is the set of partial functions such that $f \in \p$ if and only if there exists a polynomial $p$ and a Turing machine $T$ such that:
\begin{itemize}
\item If $f(x) = 1$, then $T$ halts after at most $p(|x|)$ steps and accepts.
\item If $f(x) = 0$, then $T$ halts after at most $p(|x|)$ steps and rejects.
\end{itemize}
}
\end{definition}
